Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-05 research_class/paper.tex
Initial working biblatex bibliography/citations.
Also:

- update pgfplots compat version
- generate bibliography in makefile
- add clean rule to Makefile
- add a couple initial reference files (raft, other)
- start proofread updates.

@@

\usepackage{pgfplots}
\pgfplotsset{compat=1.5}

@@

@@

\begin{abstract}
We describe the creation of a browser-based distributed peer-to-peer
application using WebRTC, PeerJS and Raft.js. WebRTC is a protocol that modern
browsers have begun to integrate which enables browser-to-browser
communication. PeerJS is a WebRTC client library and extensible signaling
server. Raft.js is an implementation in JavaScript of the Raft distributed
consensus protocol. These technologies are combined to create a chat
application that guarantees a shared, consistent and linearized view of the
chat history without relying on a single centralized server. We also create a
series of automated tests using the SlimerJS browser automation tool and use
them to show the correctness of the chat application and also to measure the
performance and scalability of the application over various cluster sizes.
\end{abstract}

@@

\section*{Acknowledgments}
I would like to thank my academic supervisor, David Levine, for his
excellent input and oversight of this project. I would also like to
thank Diego Ongaro for his amazing work on the Raft protocol and paper
which made implementing a Raft implementation a pleasure. There are
too many people involved in the creation and standardization of WebRTC
but I would like to thank them for their tireless work to make
browser-to-browser communication possible. Last but not least, I would
like to thank my family for putting up with the long nights and
weekends I spent on this project. Thanks!

@@

\end{multicols}
\end{document}

>>>>

%\usepackage[utf8]{inputenc}
\usepackage[backend=bibtex]{biblatex}

@@

\usepackage{pgfplots}
\pgfplotsset{compat=1.9}

@@

\addbibresource{references/raft.bib}
\addbibresource{references/other.bib}

@@

\begin{abstract}
We describe the creation of a browser-based distributed peer-to-peer
application using WebRTC, PeerJS and Raft.js. WebRTC is a protocol
that modern browsers have begun to integrate which enables
browser-to-browser communication. PeerJS is a WebRTC client library
and extensible signaling server. Raft.js is an implementation in
JavaScript of the Raft distributed consensus protocol. These
technologies are combined to create a chat application that guarantees
a shared, consistent and linearized view of the chat history without
relying on a single centralized server for communication. We also
create a series of automated tests using the SlimerJS browser
automation tool and use them to show the correctness of the chat
application and also to measure the performance and scalability of the
application for various cluster sizes.
\end{abstract}

@@

\section*{Acknowledgments}
I would like to thank my academic supervisor, David Levine, for his
excellent input and oversight of this project. I would also like to
thank Diego Ongaro for his amazing work on the Raft protocol and paper
\cite[p.~215]{lamport78} which made implementing
a Raft implementation a pleasure \cite{lamport78}.
There are too many people involved in the creation and standardization
of WebRTC but I would like to thank them for their tireless work to
make browser-to-browser communication possible. Last but not least,
I would like to thank my family for putting up with the long nights
and weekends I spent on this project. Thanks!

@@

\printbibliography
%\bibliographystyle{plain}
%\bibliography{references/raft,references/other}

\end{document}
